### 2014-11-13 tex/results.tex
fixing a duplicate entry in the bibg

\begin{comment}
Loops and recursive methods over symbolic variables are bounded based
on some user-provided limit. These bounds are based on some
control-flow structure of the program and are often insufficient for
analyzing programs with input of complex data types as demonstrated
in~\cite{Kiasan07,Deng:2006}. In this work we use the $k$-bounding
technique that bounds the length of a reference chain from the root of
the heap~\cite{Deng:2006}.\nsr{check this!} Note we use $k$-bounding
because it preserves the functional equivalence of \gsetxt{}, lazier,
lazier\# and \symtxt{} techniques, a fact which can be established by
induction over the length of reference chains from a given initial
state. The $n$-bounding approach restricts the total number of
references created along a certain path. There is no easy way to
compare the number of references generated by \symtxt{} and other
techniques since \symtxt{} can create many references at a single
access point in its heap summary.
\end{comment}

@@

The evaluation is performed using three Java data structure artifacts 
(i) Linked List,
(ii) Binary Search Tree, and (iii) Tree Map. 
These are the typical data structures for evaluating symbolic execution algorithms with heap initialization. The \emph{independent} variable in our
study is the algorithm for initializing symbolic references and the
$k$-bound. The initialization algorithms that we vary in our study
are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
$k$-bound for each of the algorithms. Note that $k$-bounding bounds the
length of a reference chain from the root of the heap~\cite{Deng:2006}.
We select three dependent variables and measures for our study: (i)
time, (ii) states explored, and (iii) paths generated. The \emph{time}
is the total time taken by each algorithm to explore the symbolic
execution tree as well as total constraint solving time. The
\emph{states explored} represents the number of nodes in the symbolic
execution tree, and the \emph{paths generated} represents 
the number of unique paths in the symbolic execution tree.

>>>>

\begin{comment}
Loops and recursive methods over symbolic variables are bounded based
on some user-provided limit. These bounds are based on some
control-flow structure of the program and are often insufficient for
analyzing programs with input of complex data types as demonstrated
in~\cite{Kiasan07,Kiasan06}. In this work we use the $k$-bounding
technique that bounds the length of a reference chain from the root of
the heap~\cite{Deng:2006}.\nsr{check this!} Note we use $k$-bounding
because it preserves the functional equivalence of \gsetxt{}, lazier,
lazier\# and \symtxt{} techniques, a fact which can be established by
induction over the length of reference chains from a given initial
state. The $n$-bounding approach restricts the total number of
references created along a certain path. There is no easy way to
compare the number of references generated by \symtxt{} and other
techniques since \symtxt{} can create many references at a single
access point in its heap summary.
\end{comment}

@@

The evaluation is performed using three Java data structure artifacts
(i) Linked List, (ii) Binary Search Tree, and (iii) Tree Map.  These
are the typical data structures for evaluating symbolic execution
algorithms with heap initialization. The \emph{independent} variable
in our study is the algorithm for initializing symbolic references and
the $k$-bound. The initialization algorithms that we vary in our study
are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
$k$-bound for each of the algorithms. Note that $k$-bounding bounds
the length of a reference chain from the root of the
heap~\cite{Kiasan06}.  We select three dependent variables and
measures for our study: (i) time, (ii) states explored, and (iii)
paths generated. The \emph{time} is the total time taken by each
algorithm to explore the symbolic execution tree as well as total
constraint solving time. The \emph{states explored} represents the
number of nodes in the symbolic execution tree, and the \emph{paths
  generated} represents the number of unique paths in the symbolic
execution tree.
